---
title: "Lab7_All_Regions"
author: "Rachael Cooper"
date: "10/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, include=FALSE}
library(tidyverse)
#install.packages("tidytext")
library(tidytext)
#install.packages("ggwordcloud")
library(ggwordcloud)
# install.packages("gutenbergr") 
library(gutenbergr)
#install.packages('textdata')
library(textdata)
```
/--------------------

*General Procedure*

1. Load data and necessary packages
2. Read in each article (total of 10-12), clean the data and do individual sentiment analysis and produce word clouds
3. Merge the article data together and do sentiment analysis of the entirety of the Chicago Daily Herald
4. Conduct TF-IDF analysis
5. Produce and analyze a sentiment range graph
6. Produce and analyze a word cloud, highlighting the top 50 represented words

/--------------------

```{r, include = F}
NE <- read_csv("/Users/rachael/Documents/School/Fall 2021/DS 3001/Lab7/textmining-main/article_words_NE.csv")
MW <- read_csv("/Users/rachael/Documents/School/Fall 2021/DS 3001/Lab7/textmining-main/midwest.csv")
W <- read_csv("/Users/rachael/Documents/School/Fall 2021/DS 3001/Lab7/textmining-main/west.csv")
S <- read_csv("/Users/rachael/Documents/School/Fall 2021/DS 3001/Lab7/textmining-main/south_words.csv")
```

### Climate Change by Region Analysis

#### Northeast : NY Times

```{r, echo = T}
NE[order(NE$tf_idf, decreasing = T, na.last = F),]
```

The highest tf-idf value is found to be in article 9 and the word prize. This correlates with the positive sentiment values found above in the Northeast. The word "prize" may be associated with new and novel ideas, technology, and legislation to combat the growing problem of climate change. This demonstrates that the Northeast is ahead in the change that climate change commands. In addition, another important word to consider is "city", "capital", "private", and "virginia", which are all locations and should not necessarily have any sentiment awarded to them. However, it could be that "capital" and "private" could be interpreded in regards to money and may have a positive association. It is crucial to understand the context in which the articles are talking about.

```{r, include = F}
sentiment_affin_all <- NE %>%
  inner_join(get_sentiments("afinn")) # using a inner join to match words and add the sentiment variable
sentiment_nrc_all <- NE %>%
  inner_join(get_sentiments("nrc"))
sentiment_bing_all <- NE %>%
  inner_join(get_sentiments("bing"))
```
```{r, echo = T}
table(sentiment_bing_all$sentiment)
table(sentiment_nrc_all$sentiment)
```
```{r, echo = T}
ggplot(data = sentiment_affin_all, 
       aes(x=value)
        )+
  geom_histogram()+
  ggtitle("All Articles Sentiment Range")+
  theme_minimal()
```
The sentiments of the combined articles can be seen above. The articles seemed to have generally a higher number of positive words included, though not by much. In addition, the general sentiment seemed to be more associated with trust rather than any negative connotations. This could be due to the general understanding that climate change is a real and scary issue in the Northeast. However, that could also be from articles trying to persuade readers to believe what they are saying about the climate and that it is necessary to act now. Because New York Times originates from New York city a global hub of tech, finance, and art, there is a lot of global news that may be written. For example, the positive connotations from the words could be related to the news outlet talking about the strides other countries have taken. In addition, although New York has a lot of CO2 emissions, the rest of the Northeast tends to not be constructed of very large metropolitan areas and is fairly liberal. Thus, the positive sentiment in the articles could be a result of change in legislation happening. 

The top words in the Northeast region can be seen below in the cloud graph and the table. 

```{r, echo = T}
article_words_nostop <- NE %>% distinct(word, .keep_all = TRUE) %>% anti_join(stop_words)
set.seed(42)
ggplot(article_words_nostop[1:200,], aes(label = word, size = n)
       ) +
  geom_text_wordcloud() +
  theme_minimal()
```
As seen in the graph and the table, the most common words found in all the articles were "climate" and "change", which is completely reasonable as the focus of each was climate change. However, other common words include "dr", "prize", "nations", all of which have generally positive sentiments. This corresponds to the analysis done above. Although all of the words generally have positive connotations, it is important to understand the context behind each article and see how each word is being used in the articles entirety. For example, "dr" could just be referencing the titles of people, but could be considered a positive word. In addition, "prize" could be referencing that an individual won an award when introducing their opinion in an article, and not that there is a prize pertaining to the benefit of combating climate change.

#### Midwest : Chicago Daily Herald

To provide insight into individual word importance per article, a TF-IDF analysis is created. Each article is denoted by "c#" where "#" is the particular article number it represents. From this analysis, I am able to have the ability to see the term frequency (TF) relative to the Chicago Daily Herald as a whole, and the inverse document frequency (IDF) to understand how much that specific term is present in that particular article. Sorted from highest to lowest, the tf-idf represents the most critical word to that particular article in the scheme of the Chicago Daily Herald (Corpus).

```{r}
MW[order(MW$tf_idf, decreasing=T, na.last=F),]
```
The highest tf-idf value from the output is the word "lakes" from the 8th analyzed article, or "c8", which describes the relation between climate change the rising of the Great Lakes. This demonstrates that "lakes" is important on a local level to the article and also in terms of all the articles accumulated together. Similarly, the second highest tf-idf value is "birds" from the 1st analyzed article, or "c1," which is an article describing the endangerment of bird habits from the impacts of climate change. Once again, the word "birds" is rightfully important most specifically to that article when compared to all the other articles as a whole. From this analysis, it is important to understand the frequency of words as they appear in individual articles and understand how that relates to the comparison between the variance in word frequencies across all documents.

/--------------------

```{r, include=FALSE}
# Sentiment Analysis of Combined Dataset

get_sentiments('afinn')
get_sentiments('nrc')
get_sentiments('bing')

# ------------------------

c_sentiment_affin <- MW %>%
  inner_join(get_sentiments("afinn")) %>% # using a inner join to match words and add the sentiment variable
  anti_join(stop_words)

c_sentiment_nrc <- MW %>%
  inner_join(get_sentiments("nrc"))

c_sentiment_bing <- MW %>%
  inner_join(get_sentiments("bing"))

```

```{r}
# Table format of the categorized words
table(c_sentiment_nrc$sentiment)
```

In terms of the articles as a whole and the "nrc" sentiment, there is a mostly even representation of both positive and negative words. There is a slight increase in the number of positive words, with the majority of which being classified under "trust." Relating to the topic being analyzed, climate change is a rather neutral topic that aims to bring attention to climate change awareness. In the Midwest region, the negative impact of climate change isn't as evident compared to other regions experiencing forest fires or droughts from global warming; therefore, the limited variance between the number of negative and positive is expected.

/--------------------

```{r, message=FALSE}
# Plot the sentiment range w/o stop words
ggplot(data = c_sentiment_affin, 
       aes(x=value)
        )+
  geom_histogram()+
  ggtitle("Chicago Daily Herald Sentiment Range")+
  theme_minimal()
```


In opposition to the "nrc" sentiment analysis, the "affin" sentiment analysis indicated a slighlty larger representation of negative words than positive words. The positive words are more evenly spread out among the various levels of positivity (0-3), whereas the negative words have a higher representation of the "-2" level of negativity. This can be related to the more moderate negative words that are referenced to climate change. Similarly, the positive words use more moderate references and are not overly positive comparatively. The reasoning for this can be reiterated from the section above where climate change, in terms of the Midwest, is relatively more of a neutral topic and therefore does not include either overly negative or overly positive words.

/--------------------

```{r}
# Make a word cloud w/o stop words
set.seed(42)
ggplot(MW[1:50,], aes(label = word, size = n)
       ) +
  geom_text_wordcloud() +
  theme_minimal()
```

Indicated in the word cloud, the top represented words are typical of climate change topics, specifically: climate, change, global, warming, heat. However, the words specific to the Midwest would include: lakes, water, Chicago, birds. These words are related to the area distinctive to the Midwest, such as the Great Lakes. This word cloud is visually as expected, with the inclusion of more general climate change words but also the inclusion of Midwest-specific terms.
In the table outputted below, it includes the top 25 words, sorted from most significant to least significant. 

<br/>

```{r}
# Top 25 words in the Midwest
top_25 <- MW[1:25,2] %>%
  rename(midwest.top25=word)
head(top_25)
```

/--------------------

#### West : LA Times
```{r, echo = T}
W[order(W$tf_idf, decreasing = T, na.last = F),]
```
The tf_idf was calculated for the words in these articles, using tf_idf = tf*idf, which shows the general pattern of importance of certain words. To clarify, tf is the term frequency, and idf is the inverse document frequency. The importance and tf_idf are directly related, meaning the higher the value of the tf_idf, the more important the word is in the article. Therefore, the most important words that make sense in this situtaiton in the western region (Los Angeles Times) are words such as lands, investors, water, fire, visitation, defense, military, breaking, park, etc. When the tf_idf value were arranged in descending order, it was found that the highest tf_idf value was 0.05055576 for land, which totally makes sense. Climate change has had a significant effect on our land, so it makes sense that "land" is the most important word. 

```{r}
newspaper_words_sentiment_nrc <- W %>%
  inner_join(get_sentiments("nrc"))

newspaper_words_sentiment_bing <- W %>%
  inner_join(get_sentiments("bing"))

table(newspaper_words_sentiment_bing$sentiment)
table(newspaper_words_sentiment_nrc$sentiment)
```
For most of the articles, there is a significant gap between the number of positive and negative words, which is seen in the output of each of the bing sentiment analysis. Majority of the articles (7 out of the 10) include more negative words than positive words, 213 negative vs 117 positive in total, which is almost a 2:1 ration, and that makes sense based on the topic of the articles. Climate change is a very huge issue that takes place in the world, and the best way to get people to realize this is by raising the concern and making it clear that something must be done. On top of that, by comparing the results of the nrc sentiment analysis, it can be concluded that many of the words represent fear, trust, and anticipation, as they are the top 3 most counted for words. 

```{r}
newspaper_words_sentiment_affin <- W %>%
  inner_join(get_sentiments("afinn"))
  
ggplot(data = newspaper_words_sentiment_affin, 
       aes(x=value)
        )+
  geom_histogram()+
  ggtitle("LA Times Sentiment Range")+
  theme_minimal()
```
It can be concluded that the histogram agrees with the nrc and bing sentiment analysis. This can be seen by the high negativity, higher word count below 0, and low positivity, lower word count above 0. Therefore, the words are more skewed to the left, indicating that the western region articles tend to be more negative. 

```{r}
#LA times word cloud 

ggplot(W[1:50,], aes(label = word, size = n)
       ) +
  geom_text_wordcloud() +
  theme_minimal()
```
Based on the output of the word cloud that corresponds to the LA Times newspaper, which in this case is the corpus formed by combining the articles (documents), the most commonly said words are those that appear bolder, larger, an more often. Therefore, it seems that words such as "drought", "water","fire", and "climate" are mentioned quite often in Los Angeles Times Newspaper articles about climate change. This completely makes sense because in the western region, especially California, they often suffer from droughts, and wild fires. One of the most surprising words for me was "change" as I thought this word would possibly appear bolder and larger, because it would make sense that this word would be used often in articles about climate CHANGE. 




#### South : Richmond Times Dispatch



